---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# quartabs

<!-- badges: start -->
[![R-CMD-check](https://github.com/sayuks/quartabs/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/sayuks/quartabs/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/sayuks/quartabs/graph/badge.svg)](https://app.codecov.io/gh/sayuks/quartabs)
[![lint.yaml](https://github.com/sayuks/quartabs/actions/workflows/lint.yaml/badge.svg)](https://github.com/sayuks/quartabs/actions/workflows/lint.yaml)
<!-- badges: end -->

Dynamically Generate [Tabset Panels](https://quarto.org/docs/output-formats/html-basics.html#tabsets) in a Quarto HTML Document.

## Installation

``` r
install.packages("quartabs")
```

You can install the development version of quartabs from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("sayuks/quartabs")
```

## Examples

`render_tabset()` takes a data frame as input and outputs the markdown that generates the [tabset](https://quarto.org/docs/output-formats/html-basics.html#tabsets) to stdout (console).

**In the actual .qmd file, specify the chunk option `results: asis`.**

```{r}
library(quartabs)

data.frame(
  tab = c("A", "B"),
  value = c("Tab content for A", "Tab content for B")
) |>
  render_tabset(tab, value)
```

See [Get started](https://sayuks.github.io/quartabs/vignettes/get_started.html) for details.

## Code of Conduct

Please note that the quartabs project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
